Imposing a Weight Norm Constraint for Neuro-Adaptive Control

### 2025-06-10 presentation/presentation.tex
ppt final update for security check

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Extra packages for the demo:
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{ragged2e}
\usepackage{schemabloc}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% \usepackage{calc}
% \usepackage{svg}
% \usepackage{media9}             %pdflatex, latex+dvips+ps2pdf, xelatex
% \usepackage{multimedia}
% \usepackage{animate}

@@

\logo{
  \vspace{-.7cm}%
  \includegraphics[height=0.3cm]{assets/kaist_logo.png}
  \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.png}
  \hspace{.6cm}%
  }

@@

  \begin{figure}
    \includegraphics[width=0.25\textwidth]{figures/KAIST-hi.png}
  \end{figure}

@@

\subsection{Literature Review}

\begin{frame}{\insertsubsectionhead}{Boundedness of NN Weights}

  In general, the NN outputs are bounded by limiting the maximum amplitude of the NN weights.

  \begin{enumerate}
    \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{Projection Operator}

          \begin{itemize}
            \item Cats 
            \item Dogs 
            \item Birds
          \end{itemize}

        \column{0.49\textwidth}
          \begin{figure}
            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
          \end{figure}
      \end{columns}

      \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{$\epsilon$-modification, and $\sigma$-modification}

          \begin{itemize}
            \item Cats 
            \item Dogs 
            \item Birds
          \end{itemize}

        \column{0.49\textwidth}
          \begin{figure}
            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
          \end{figure}
      \end{columns}
  \end{enumerate}
\end{frame}

\subsection{Literature Review}

\begin{frame}{\insertsubsectionhead}{Input Saturation}

  The input saturation is generally handled using an auxiliary system.

  \begin{enumerate}
    \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{Auxiliary Systems}

          \begin{itemize}
            \item Cats 
            \item Dogs 
            \item Birds
          \end{itemize}

        \column{0.49\textwidth}
          \begin{figure}
            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
          \end{figure}
      \end{columns}

      \begin{columns}[T,onlytextwidth]
        \column{0.49\textwidth}
          \item \textbf{Second?}

          \begin{itemize}
            \item Cats 
            \item Dogs 
            \item Birds
          \end{itemize}

        \column{0.49\textwidth}
          \begin{figure}
            \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
          \end{figure}
      \end{columns}
  \end{enumerate}
\end{frame}

@@

      \textbf{Target 2-link Robotic Manipulator System}:
      \begin{itemize}
        \item Control input saturation function $\mysat(\cdot)$.
        \item Desired trajectory $\mv{q}_d$ is given.
      \end{itemize}
        \begin{equation}
          \mm{M}\ddq + \mm{V}_m\dq + \mv{F} + \mv{G} + \mv{\tau}_d
          =
          \mysat(\mv{\tau})
        \end{equation}

      \textbf{Control Input}:
      \begin{itemize}
        \item NN's output $\mv{\Phi}$ is used as the control input.
        \item Consists of the estimated NN weights $\estwth$.
      \end{itemize}
      \begin{equation}
        \mv{\tau} := \mv{\Phi}(\mv{q}_n; \estwth)
      \end{equation}

      \textbf{Deep Neural Network (DNN)}:
      \begin{itemize}
        \item $k$ layers with $\estwth_i:=\myvec(\estwV_i)$.
        \item Activation function: $\phi(\cdot):=tanh(\cdot)$.
        \begin{equation}
          \mv{\Phi}(\mv{q}_n; \estwth)
          :=
          \begin{cases}
              \estwV_i^\top \act_i(\estNN_{i-1}), 
              &
              i\in\{1,\dots ,k\},
              \\
              \estwV_0^\top {\q}_n,
              &
              i=0
              ,
          \end{cases}
        \end{equation}
      \end{itemize}

@@

    \begin{itemize}
      \item \textbf{Find} NN weights $\estwth$,
      \item That \textbf{minimize} objective function $J(\cdot)$,
        \begin{equation}
          J(\mv{r}) := \frac{1}{2} \mv{r}^\top \mv{r}.
        \end{equation}
        \begin{itemize}
          \item where $\mv{r} := \ddt\mv{e} + \Lambda\mv{e}$ is the filtered tracking error,
        \end{itemize}
      \item while satisfying the following \textbf{constraints}:
        \begin{itemize}
          \item Boundedness of the NN weights $\estwth$.
          \item Saturation of the control input $\mv{\tau}$.
        \end{itemize}
    \end{itemize}

@@

      \begin{itemize}
        \item \textbf{Weight Boundedness}: 
          \begin{equation}
            c_{\theta_i}
            :=
            \norm{\estwth_i}^2 - \bar{\theta_i}^2 \le 0
            , 
            \forall i\in\{0,\ldots,k\}
          \end{equation}

        \item \textbf{Control Input Saturation}: 
          \begin{itemize}
            \item Input bound constraint:
            \begin{equation}
              c_{\overline{\tau}_i}
              :=
              \tau_i - \overline{\tau_i}
              \le 
              0
              ,
              c_{\underline{\tau}_i}
              :=
              \underline{\tau_i} - \tau_i
              \le 
              0
            \end{equation}
            \item Input norm constraint:
            \begin{equation}
              c_{\mv{\tau}}
              :=
              \norm{\mv{\tau}}^2 - \overline{\tau}^2
              \le
              0
            \end{equation}
        \end{itemize}
      \end{itemize}

@@

@@

      \centering
      \begin{minipage}{0.9\textwidth}%
        \begin{block}{Optimization Problem}%

          \begin{equation}
            \begin{matrix}
              \min_{\estwth} J(\mv{r};\estwth)
              \\\ \\
              \text{s.t. } c_{j}(\estwth) 
              \le 
              0
              ,
              \forall j\in\mathcal{J}
            \end{matrix}
          \end{equation}

        \end{block}
      \end{minipage}

      \centering
      \begin{minipage}{0.9\textwidth}%
        \begin{block}{MinMax Problem}%

          \begin{equation}
            \begin{matrix}
              \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{J}}} L(\cdot)
              \\\ \\
              \text{where }
              L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{J}})
              :=
              J(\mv{r};\estwth)
              +
              \sum_{j\in\mathcal{J}} \lambda_j c_j(\estwth)
            \end{matrix}
          \end{equation}

        \end{block}
      \end{minipage}

@@

\begin{frame}{\insertsubsectionhead}{Steepest Descent/Ascent Method}

      \begin{minipage}{0.9\textwidth}%
        For the min/max problem, the steepest descent/ascent method is used to derive the adaptation law.
      \end{minipage}

      \vspace{0.5cm}

      \begin{minipage}{0.9\textwidth}%
        \textbf{Steepest Descent Method for $\estwth$}:
        \begin{equation}
          \ddtt\estwth
          =
          -\alpha 
          \pptfrac{L}{\estwth}
        \end{equation}

        \textbf{Steepest Ascent Method for $\lambda_j$}:
        \begin{equation}
          \ddtt\lambda_j = 
        \end{equation}
      \end{minipage}

      \centering
        \begin{block}{Adaptation Law}%

        \begin{subequations}
            \begin{align}
                    \ddt {{\estwth}}
                    &
                    =
                    -\alpha 
                    \ppfrac{L}{{\estwth}}
                    =-\alpha 
                    \left(
                        \ppfrac{J}{{\estwth}}
                        +
                        \sum_{j\in\mathcal{I}}
                        \lambda_j 
                        \ppfrac{c_j}{\estwth}
                    \right),
                    \\
                    \ddt\lambda_j
                    & 
                    = 
                    \beta_j
                    \ppfrac{L}{\lambda_j} 
                    = 
                    \beta_j c_j ,
                    \quad\quad\quad\quad      \      
                    \forall j\in\mathcal I,
                    \\
                    \lambda_j 
                    & 
                    = 
                    \max(\lambda_j,0) ,
            \end{align}
        \end{subequations}

  \begin{block}{Theorem 1}
    For the dynamical system described in (1), the neuro-adaptive controller in (2) with the weight adaptation laws in (12) ensure the boundedness of the filtered error $\mv{r}$ and the weight estimate $\estwth$, under the control input constraints satisfying Assumption 1 and 2. This holds under the weight norm constraint (5).
  \end{block}

  \begin{exampleblock}{Assumption 1}
    The constraint functions $c_j(\estwth),\forall j\in\mathcal{I}$, are convex in the $\tau$-space and satisfy $c_j(\estwth)\le0$ and $c_j(\idealwth)\le0$.
  \end{exampleblock}

  \begin{exampleblock}{Assumption 2}
    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap. 12 Def. 12.1]{Nocedal:2006aa}.
  \end{exampleblock}

  Proof of Theorem 1 is omitted due to space limitations. The detailed proof can be found in \cite{}.

\section{Numerical Validation}

\subsection{Simulation Setup}
\begin{frame}{\insertsubsectionhead}{2-Link Robotic Manipulator}

  \begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/exp_set.drawio.png}
    \caption{2-Link Robotic Manipulator}
  \end{figure}

  \let\thefootnote\relax\footnote{
    \textit{Notations}: 
      $\mv{q}$: Joint position, $\mv{\dot{q}}$: Joint velocity, $\mv{\tau}$: Control input, $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector.
  }

@@

\begin{frame}{Representative Simulation Results}

@@

@@

\begin{frame}{Box-and-Whisker Plots}

  \begin{columns}
    \column{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{figures/BoxWhisker.drawio.png}
        \caption{Parameter dependencies of the proposed method.}
      \end{figure}

    \column{0.5\textwidth}
      \begin{table}
        \caption{Largest cities in the world (source: Wikipedia)}
        \begin{tabular}{@{} lr @{}}
          \toprule
          City & Population\\
          \midrule
          Mexico City & 20,116,842\\
          Shanghai & 19,210,000\\
          Peking & 15,796,450\\
          Istanbul & 14,160,467\\
          \bottomrule
        \end{tabular}
    \end{table}

\begin{frame}{Parameter Dependencies}

@@

    \column{0.33\textwidth}
      \begin{figure}      
        \includegraphics[width=0.99\textwidth]{figures/ECC/fig9.eps}
        \caption{Weight norms of NAC-L2}
      \end{figure}

@@

@@

  The weight norms of the proposed method (NAC-CO) are bounded, while ...

\begin{frame}{Parameter Dependencies}

    \column{0.33\textwidth}
      \begin{figure}      
        \includegraphics[width=0.99\textwidth]{figures/ECC/fig6.eps}
        \caption{Tracking error of NAC-L2}
      \end{figure}

@@

  The Tracking error ...

@@

@@

  \bibliography{../template/refs}
  \bibliographystyle{ieeetr}

>>>>

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% Extra packages for the demo:
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{ragged2e}
\usepackage{schemabloc}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

\usepackage{multirow}

% \usepackage{calc}
% \usepackage{svg}
% \usepackage{media9}             %pdflatex, latex+dvips+ps2pdf, xelatex
% \usepackage{multimedia}
% \usepackage{animate}

@@

% \logo{
%   \vspace{-.7cm}%
%   \includegraphics[height=0.3cm]{assets/kaist_logo.png}
%   \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.png}
%   \hspace{.6cm}%
%   }

@@

@@

% \subsection{Literature Review}

% \begin{frame}{\insertsubsectionhead}{Boundedness of NN Weights}

%   In general, the NN outputs are bounded by limiting the maximum amplitude of the NN weights.

%   \begin{enumerate}
%     \begin{columns}[T,onlytextwidth]
%         \column{0.49\textwidth}
%           \item \textbf{Projection Operator}

%           \begin{itemize}
%             \item Cats 
%             \item Dogs 
%             \item Birds
%           \end{itemize}

%         \column{0.49\textwidth}
%           \begin{figure}
%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
%           \end{figure}
%       \end{columns}

%       \begin{columns}[T,onlytextwidth]
%         \column{0.49\textwidth}
%           \item \textbf{$\epsilon$-modification, and $\sigma$-modification}

%           \begin{itemize}
%             \item Cats 
%             \item Dogs 
%             \item Birds
%           \end{itemize}

%         \column{0.49\textwidth}
%           \begin{figure}
%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
%           \end{figure}
%       \end{columns}
%   \end{enumerate}
% \end{frame}

% \begin{frame}{\insertsubsectionhead}{Input Saturation}

%   The input saturation is generally handled using an auxiliary system.

%   \begin{enumerate}
%     \begin{columns}[T,onlytextwidth]
%         \column{0.49\textwidth}
%           \item \textbf{Auxiliary Systems}

%           \begin{itemize}
%             \item Cats 
%             \item Dogs 
%             \item Birds
%           \end{itemize}

%         \column{0.49\textwidth}
%           \begin{figure}
%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
%           \end{figure}
%       \end{columns}

%       \begin{columns}[T,onlytextwidth]
%         \column{0.49\textwidth}
%           \item \textbf{Second?}

%           \begin{itemize}
%             \item Cats 
%             \item Dogs 
%             \item Birds
%           \end{itemize}

%         \column{0.49\textwidth}
%           \begin{figure}
%             \includegraphics[width=0.4\textwidth]{figures/KAIST-hi.png}
%           \end{figure}
%       \end{columns}
%   \end{enumerate}
% \end{frame}

@@

      \textbf{Target Two-link Robotic Manipulator System}:
      \begin{itemize}
        \item Control input saturation function $\mysat(\cdot)$.
        \item Desired trajectory $\mv{q}_d$ is given.
      \end{itemize}
        \begin{equation}\label{eq:sys}
          \mm{M}\ddq + \mm{V}_m\dq + \mv{F} + \mv{G} + \mv{\tau}_d
          =
          \mysat(\mv{\tau})
        \end{equation}

      \textbf{Control Input}:
      \begin{itemize}
        \item NN's output $\mv{\Phi}$ is used as the control input.
        \item Consists of the estimated NN weights $\estwth$.
      \end{itemize}
      \begin{equation}\label{eq:input}
        \mv{\tau} := \mv{\Phi}(\mv{q}_n; \estwth)
      \end{equation}

      \textbf{Deep Neural Network (DNN)}:
      \begin{itemize}
        \item $k$ layers with $\estwth_i:=\myvec(\estwV_i)$.
        \item Activation function: $\phi(\cdot):=tanh(\cdot)$.
        \begin{equation}\label{eq:NN}
          \mv{\Phi}(\mv{q}_n; \estwth)
          :=
          \begin{cases}
              \estwV_i^\top \act_i(\estNN_{i-1}), 
              &
              i\in\{1,\dots ,k\},
              \\
              \estwV_0^\top {\q}_n,
              &
              i=0
              ,
          \end{cases}
        \end{equation}
      \end{itemize}

@@

    \begin{itemize}
      \item \textbf{Find} NN weights $\estwth$,
      \item That \textbf{minimize} objective function $J(\cdot)$,
        \begin{equation}\label{eq:obj}
          J(\mv{r};\estwth)
          := 
          \frac{1}{2} \mv{r}^\top \mv{r}.
        \end{equation}
        \begin{itemize}
          \item where $\mv{r} := \ddt\mv{e} + \Lambda\mv{e}$ is the filtered tracking error,
        \end{itemize}
      \item while satisfying the following \textbf{constraints}:
        \begin{itemize}
          \item Boundedness of the NN weights $\estwth$.
          \item Saturation of the control input $\mv{\tau}$.
        \end{itemize}
    \end{itemize}

@@

      \begin{itemize}
        \item \textbf{Weight Boundedness for Each Layer}: 
          \begin{equation}\label{eq:cstr:weight}
            c_{\theta_i}(\estwth)
            :=
            \norm{\estwth_i}^2 - \overline{\theta_i}^2 \le 0
            , 
            \forall i\in\{0,\ldots,k\}
          \end{equation}

        \item \textbf{Convex control Input Saturation}: 
          \begin{itemize}
            \item Input bound constraint:
            \begin{equation}\label{eq:cstr:input_bound}
              c_{\overline{\tau}_i}(\estwth)
              :=
              \tau_i - \overline{\tau_i}
              \le 
              0
              ,
              \quad
              c_{\underline{\tau}_i}(\estwth)
              :=
              \underline{\tau_i} - \tau_i
              \le 
              0
            \end{equation}
            \item Input norm constraint:
            \begin{equation}\label{eq:cstr:input_norm}
              c_{\mv{\tau}}(\estwth)
              :=
              \norm{\mv{\tau}}^2 - \overline{\tau}^2
              \le
              0
            \end{equation}
        \end{itemize}
      \end{itemize}

@@

  \textbf{Original Optimization Problem}

  \begin{itemize}
    \item Constrained optimization problem to minimize the tracking error.
    \item Inequality constraints $c_j(\estwth) \le 0$ for $j\in\mathcal{I}$.
  \end{itemize}

    \begin{equation}\label{eq:opt_problem}
      \begin{matrix}
        \min_{\estwth} J(\mv{r};\estwth)
        \\\ \\
        \text{s.t. } c_{j}(\estwth) 
        \le 
        0
        ,
        \forall j\in\mathcal{I}
      \end{matrix}
    \end{equation}

  \textbf{Define Lagrangian Function}

  \begin{equation}\label{eq:lagrangian}
      L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
      :=
      J(\mv{r};\estwth)
      +
      \sum_{j\in\mathcal{I}} \lambda_j c_j(\estwth)
  \end{equation}

  \textbf{Dual Problem}
  \begin{itemize}
    \item The dual problem is to minimize the Lagrangian function with respect to the NN weights $\estwth$, while maximizing the Lagrange multipliers $\lambda_j$.
    \item The Lagrange multipliers $\lambda_j$ are non-negative, \ie $\lambda_j \ge 0$.
  \end{itemize}

  \begin{equation}\label{eq:dual_problem}
    \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{I}}} 
    L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
  \end{equation}

\begin{frame}{\insertsubsectionhead}{Gradient Descent/Ascent Method}

  For the dual problem, 
  \begin{equation}
    \min_{\estwth}\max_{[\lambda_j]_{j\in\mathcal{I}}} 
    L(\mv{r},\estwth,[\lambda_j]_{j\in\mathcal{I}})
    ,
  \end{equation}
  the first-order gradient descent/ascent method is used to derive the adaptation law.

  \centering
  \begin{minipage}{0.6\textwidth}%

    \begin{block}{Adaptation Law}%

    \textbf{Gradient Descent Method for $\estwth$}:
    \begin{equation}\label{eq:adaptation_law:1}
      \ddt {{\estwth}}
      =
      -\alpha 
      \ppfrac{L}{{\estwth}}
      =-\alpha 
      \left(
          \ppfrac{J}{{\estwth}}
          +
          \sum_{j\in\mathcal{I}}
          \lambda_j 
          \ppfrac{c_j}{\estwth}
      \right),
    \end{equation}

    \textbf{Gradient Ascent Method for $\lambda_j, \forall j\in\mathcal I$}:
    \begin{equation}\label{eq:adaptation_law:2}
      \ddt\lambda_j
      = 
      \beta_j
      \ppfrac{L}{\lambda_j} 
      = 
      \beta_j c_j ,
    \end{equation}

    For non-negativity of the Lagrange multipliers,
    \begin{equation}\label{eq:adaptation_law:3}
      \lambda_j
      \leftarrow
      \max(\lambda_j,0)
      .
    \end{equation}

    % \begin{subequations}
    %     \begin{align}
    %       \ddt {{\estwth}}
    %       &
    %       =
    %       -\alpha 
    %       \ppfrac{L}{{\estwth}}
    %       =-\alpha 
    %       \left(
    %           \ppfrac{J}{{\estwth}}
    %           +
    %           \sum_{j\in\mathcal{I}}
    %           \lambda_j 
    %           \ppfrac{c_j}{\estwth}
    %       \right),
    %       \\
    %       \ddt\lambda_j
    %       & 
    %       = 
    %       \beta_j
    %       \ppfrac{L}{\lambda_j} 
    %       = 
    %       \beta_j c_j ,
    %       \quad\quad\quad\quad      \      
    %       \forall j\in\mathcal I,
    %       \\
    %       \lambda_j
    %       &
    %       \leftarrow
    %       \max(\lambda_j,0)
    %     \end{align}
    % \end{subequations}

    \end{block}
  \end{minipage}
\end{frame}

  \begin{block}{Theorem 1 \cite{Ryu:2025aa}}
    For the dynamical system described in \eqref{eq:sys}, the neuro-adaptive controller in \eqref{eq:input} with the weight adaptation laws in \eqref{eq:adaptation_law:1}, \eqref{eq:adaptation_law:2} and \eqref{eq:adaptation_law:3} ensure the boundedness of the filtered error $\mv{r}$ and the weight estimate $\estwth$, under the control input constraints satisfying Assumption 1 and 2. This holds under the weight norm constraint \eqref{eq:cstr:weight}.
  \end{block}

  \begin{exampleblock}{Assumption 1 (Convex Input Constraint)}
    The constraint functions $c_j(\estwth),\forall j\in\mathcal{I}$, are convex in the $\tau$-space and satisfy $c_j(\estwth)\le0$ and $c_j(\idealwth)\le0$.
  \end{exampleblock}

  \begin{exampleblock}{Assumption 2, Linear Independence Constraint Qualification (LICQ)}
    The selected constraints satisfy the Linear Independence Constraint Qualification (LICQ) \cite[Chap. 12 Def. 12.1]{Nocedal:2006aa}.
  \end{exampleblock}

  Proof of Theorem 1 is omitted due to space limitations. The detailed proof can be found in \cite{Ryu:2025aa}.

\section{Experimental Validation}

\subsection{Simulation Setup}

\begin{frame}{\insertsubsectionhead}{Two-Link Robotic Manipulator}

@@

      \column{.45\textwidth}

        \textbf{Target System}:

        \begin{equation*}
          \mm{M}\ddq + \mm{V}_m\dq + \mv{F} + \mv{G} + \mv{\tau}_d
          =
          \mv{\tau}
        \end{equation*}

        \begin{figure}
          \centering
          \includegraphics[width=.99\textwidth]{figures/RobotModel.drawio.png}
          \caption{Two-link robotic manipulator model.}
        \end{figure}

      \column{.55\textwidth}

        \textbf{Desired Trajectory}:

        \begin{equation}
          \qd
          =
          \begin{bmatrix}
              {q_d}_1\\
              {q_d}_2
          \end{bmatrix}
          = 
          \begin{bmatrix}
              +\cos(
                  \tfrac{\pi}{2}t
              ) + 1 \\
              -\cos(
                  \tfrac{\pi}{2}t
              ) - 1 
          \end{bmatrix}
          .
      \end{equation}

      \textbf{System Model Parameters}:

      \begin{table}
        \renewcommand{\arraystretch}{1.3}
        \caption{System model parameters.}
        \centering
        \begin{tabular}{c m{5em} c c c }
        \hline
        \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
        \hline
        \hline 
        $m_p$ & Mass & 23.902 kg & 3.88 kg \\
        \hline
        $l_p$  & Length & 0.45 m & 0.45 m \\
        \hline
        ${l_c}_p$ & COM & 0.091 m & 0.048 m \\
        \hline
        $b_p$   & Viscous coef. &  2.288 Nms & 0.172 Nms \\
        \hline
        ${f_c}_p$  & Friction coef. & 7.17 Nm & 1.734 Nm \\
        \hline
        \end{tabular}
        \label{table: system parameters}
      \end{table}

@@

\begin{frame}{\insertsubsectionhead}{Controllers for Comparative Study}

    \begin{itemize}
      \item NAC-CO denotes the proposed controller based on constrained optimization.
      \item For NAC-L2 and NAC-eMod, the stabilizing terms $-\lambda\estwth$ and $\rho\norm{\tilde{\mv{z}}}\estwth$ ensures the boundedness of the NN weights
    \end{itemize}

    \begin{table}
      \renewcommand{\arraystretch}{1.5}
      % \caption{Controller Properties.}
      \centering
      \begin{tabular}{c m{20em} c c c }
      \hline
      \textbf{Name} & \textbf{Description} & \textbf{Adaptation Law} \\
      \hline
      \hline 
        \multirow{2}{*}{NAC-CO} & Constrained Optimization-based NAC & 
      $
        \ddt\estwth = -\alpha \left(\ppfrac{L}{\estwth}+\sum_{j\in\mathcal{I}}\lambda_j\ppfrac{c_j}{\estwth}\right)
      $ 
      \\
        (proposed) & ($\beta_j$ determines $\lambda_j$ adaptation speed) &
      $
        \ddt\lambda_j = \beta_j c_j, \lambda_j \leftarrow \max(\lambda_j,0)
      $
      \\
      \hline
      \multirow{2}{*}{NAC-L2} & NAC with $L_2$-regularization & \multirow{2}{*}
      {$
        \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\lambda\estwth\right)
      $}
      \\
        & ($\lambda\in\R_{>0}$ stabilizes $\estwth$ towards origin) &
      \\
      \hline
      \multirow{2}{*}{NAC-eMod} & NAC with $\epsilon$-modification & \multirow{2}{*}
      {$
        \ddt\estwth = -\alpha \left(\ppfrac{J}{\estwth}+\rho\norm{\tilde{\mv{z}}}\estwth\right)
      $}
      \\
      & ($\rho$ stabilizes proportionally to the error $\tilde{\mv{z}}$) &
      \\
      \hline
      \end{tabular}
      \label{table:sys:param}
    \end{table}

    \centering
    \begin{minipage}{0.75\textwidth}
      \begin{block}{Simulation Objective}
        By varying the parameters, \ie $\beta_j$, $\lambda$, and $\rho$, the parameter dependencies will be investigated.
      \end{block}
    \end{minipage}

@@

% \begin{frame}{Representative Simulation Results}

@@

% \end{frame}

\begin{frame}{\insertsubsectionhead}{Box-and-Whisker Plots}

  \begin{columns}
    \column{0.55\textwidth}

      \textbf{Parameter Dependencies Investigation}:

      \begin{itemize}
        \item The parameters ranged from 0.001 to 1 across 10 samples.
        \item NAC-CO (proposed) shows the best performance and low variance.
        \item NAC-L2 shows the worst performance with high variance.
      \end{itemize}

      \begin{figure}
        \includegraphics[width=.99\textwidth]{figures/BoxWhisker.drawio.png}
        \caption{Parameter dependencies of the proposed method.}
      \end{figure}

    \begin{table}[!t]
      \renewcommand{\arraystretch}{1.1}
      % \caption{Quantitative comparison of square root of tracking ISE.}
      \centering
      \begin{tabular}{c c c c }
      \hline
      & \textbf{NAC-L2}\!&\!\textbf{NAC-eMod}\!&\!\textbf{NAC-CO} (proposed) 
      \\
      \hline
      \hline 
        Maximum\!&\!$11.1753\!\times\!10^{-3}$\!&\!$0.5603\!\times\!10^{-3}$\!&\!$0.3439\!\times\!10^{-3}$\!\\
      \hline
        Median\!&\!$0.5898\!\times\!10^{-3}$\!&\!$0.5519\!\times\!10^{-3}$\!&\!$0.3240\!\times\!10^{-3}$\!\\
      \hline
        Minimum\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.5434\!\times\!10^{-3}$\!&\!$0.3235\!\times\!10^{-3}$\!\\
      \hline
      \end{tabular}
      \label{table: error norm}
    \end{table}

    \let\thefootnote\relax\footnote{
      Squared root of the tracking error ISE (Integral of Squared Error) is used, \ie $\sqrt{\int_0^T \norm{\mv{r}}^2\,\der t}$, where $T$ denotes a simulation termination time.
    }

@@

\begin{frame}{\insertsubsectionhead}{Weight Norms}

@@

      \begin{figure}      
        \includegraphics[width=0.99\textwidth]{figures/ECC/fig9.eps}
        \caption{Weight norms of NAC-L2}
      \end{figure}

@@

  \begin{itemize}
    \item NAC-CO (proposed) showed the weight norms are bounded under pre-defined constraint $\overline{\theta}=20$.
    \item NAC-L2 and NAC-eMod showed the bounded weight norms, but they depended on the parameters $\lambda$ and $\rho$, respectively.
    \item As the parameters $\lambda$ and $\rho$ increase, the weight norms of NAC-L2 and NAC-eMod biased towards the origin, which may lead to suboptimal performance.
    \item In addition, NAC-CO tracked the desired trajectory with a smaller weight norm than NAC-L2 and NAC-eMod.
  \end{itemize}

\begin{frame}{\insertsubsectionhead}{Tracking Performance}

@@

      \begin{figure}      
        \includegraphics[width=0.99\textwidth]{figures/ECC/fig6.eps}
        \caption{Tracking error of NAC-L2}
      \end{figure}

@@

  \begin{itemize}
    \item NAC-CO (proposed) outperformed NAC-L2 and NAC-eMod in terms of tracking performance.
    \item As the weights are biased towards the origin, the tracking performance of NAC-L2 and NAC-eMod deteriorated.
  \end{itemize}

@@

% \subsection{Simulation Setup}

% \begin{frame}{\insertsubsectionhead}{Two-Link Robotic Manipulator}

%     \begin{columns}

%       \column{.55\textwidth}
%         \begin{figure}
%           \centering
%           \includegraphics[width=.85\textwidth]{figures/RobotModel.drawio.png}
%           \caption{Two-Link Robotic Manipulator}
%         \end{figure}

%       \column{.5\textwidth}

%         \begin{table}[t]
%             \renewcommand{\arraystretch}{1.3}
%             \caption{Two-link robotic manipulator's parameters.}
%             \centering
%             \begin{tabular}{c m{9.5em} c c c }
%             % \begin{tabular}{c c c c c}
%             \hline
%             \textbf{Symbol} & \textbf{Description} & \textbf{Value} \\
%             \hline
%             \hline 
%             $m_1,m_2$ & Mass & 2.465 kg \\
%             \hline
%             $l_1,l_2$  & Length & 0.2 m \\  
%             \hline
%             ${l_c}_1,{l_c}_2$ & Center of mass & 0.139 m \\
%             \hline
%             $I_1,I_2$  & Inertia & 0.069 kgm\textsuperscript{2} \\
%             \hline
%             \end{tabular}
%         \end{table}

%     \end{columns}

% \end{frame}

@@

  \bibliography{localRefs}
  \bibliographystyle{IEEEtran}
